---
title: "h&m_Purchase_predict"
author: "H"
date: "2/8/2022"
output: html_document
---


```{r}
library(data.table)
```

```{r}
article <- fread("articles.csv", header = TRUE)
```

```{r}
customer <- fread("customers.csv", header = TRUE)
```

```{r}
sample_submission <- fread("sample_submission.csv", header = TRUE)
```

```{r}
transaction_train <- fread("transactions_train.csv", header = TRUE)
```

#### EDA 
#### Data cleaning 
```{r}
str(article)
```
```{r}
is.na(article)
```

```{r}
library(tidyr)
```
####Delete NA  from age, fashion news frequency in Customer data 

```{r}
customer <- customer %>% drop_na(age)
```
```{r}
customer
```
```{r}
sum(is.na(customer$age))
```
```{r}
sum(is.na(customer$fashion_news_frequency))

```


```{r}
str(sample_submission)
```

```{r}
summary(transaction_train)
```
```{r}
transaction_train$t_dat <- as.Date(transaction_train$t_dat)
```

#### 1-1 Product distribution
```{r}
summary(article)
```
```{r}
library(dplyr)
library(ggplot2)
library(wesanderson)
```
```{r}
index <- article %>% group_by(Categories = index_group_name) %>% summarise(Count = n()) %>% mutate(Total = sum(Count), percent = Count/Total)
```
```{r}
index
```
#### Top 10 product 

```{r}
productType <- article %>% group_by(product_name =product_type_name) %>% summarise(Count = n()) %>% arrange(desc(Count)) %>% head(10)

```
```{r}
productType
```
```{r}
names(wes_palettes)
```


### Visualization 
```{r}
ggplot(aes(x= "", y= percent, fill =Categories), data= index) +geom_bar(stat = "identity", position = position_fill()) +
  coord_polar("y") + geom_text(aes(x= 1.25, label =Count ), position = position_fill(vjust= 0.5)) + theme(axis.title.x = element_blank(), axis.title.y = element_blank(), plot.title = element_text())  + scale_fill_manual(values=wes_palette(n=5, name="Darjeeling2"))
```
### majority of article categories is ladieswear and baby/children cloth. 
```{r}
ggplot(data= productType ,aes(x= product_name, y= Count)) + geom_bar(stat = "identity", fill = "Blue")
```
### The most frequent product types are Trousers and Dress Sweater and T-shirts are following. 
### 1-2 customer demograhpic 

```{r}
customer
```
#### check missing data 

```{r}
customer$fashion_news_frequency
```


```{r}
customer$fashion_news_frequency[customer$fashion_news_frequency == ""] <- NA

```
```{r}
customer$club_member_status[customer$club_member_status == ""] <- NA
```

```{r}
customer <- customer %>% drop_na(club_member_status, fashion_news_frequency)
```

```{r}
member <- customer %>% group_by(club_member_status) %>% summarise(Count = n())
```
```{r}
member
```
```{r}
frequency <- customer %>% group_by(fashion_news_frequency) %>% summarise(Count =n())
```


```{r}
frequency
```
#### We can see we have two type of none, "NONE" and "None" , so I change "NONE" -> None


```{r}
customer$fashion_news_frequency[customer$fashion_news_frequency == "NONE"] <- "None"

```
```{r}
frequency
```
```{r}
agegroup <- customer %>%  group_by(agegroup = cut(age, breaks = seq(16,75, by =5)), club_member_status, fashion_news_frequency) %>% drop_na(agegroup) %>% summarise(Count =n())
```
```{r}
agegroup
```
```{r}
summary(agegroup)
```
```{r}
ggplot(aes(x =agegroup ,y = Count, fill = fashion_news_frequency), data = agegroup)+geom_bar(stat = "identity") +scale_fill_manual(values = wes_palette(n=3, name="Moonrise1"))
```
```{r}
options(scipen = 100)

```
```{r}
ggplot(aes(x =agegroup ,y = Count, fill = club_member_status), data = agegroup)+geom_bar(stat = "identity") +scale_fill_manual(values = wes_palette(n=3, name="Moonrise1"))
```
#### aged 20-30 is the major customers in Most age group activate club members, but mostly don't get fashion news frequently. 



```{r}
names(wes_palettes)
```
####1-3 EDA transaction train 

```{r}
transaction_train
```
#### Aggregate data 
```{r}
library(lubridate)
```

```{r}
sum(is.na(transaction_train$article_id))
```
#### Customer ID =  00007d2de826758b65a93dd24ce629ed66842531df6699338c5570910a014cc2		


```{r}
customer_item <- transaction_train %>% select(t_dat, customer_id, article_id)
```
```{r}
customer_item
```
```{r}
customer_1 <- customer_item %>% filter(customer_id == "00007d2de826758b65a93dd24ce629ed66842531df6699338c5570910a014cc2") %>% group_by(Date = floor_date(t_dat, "month"), article_id)  %>% summarise(Count = n())

```

```{r}
customer_1
```
```{r}
summary(customer_1)
```
#### Customer ID =  00007d2de826758b65a93dd24ce629ed66842531df6699338c5570910a014cc2	bought total 110 items from Sep 2018 to 2020 May.

### Article type 
```{r}
article
```


```{r}
articletype <- article %>% select(article_id, prod_name, product_type_name, product_group_name, index_name, colour_group_name) 
```
```{r}
customer_1_article <- merge(x =customer_1, y= articletype, by= "article_id") %>% arrange((Date))
```
```{r}
customer_1_article
```
```{r}
unique(customer_1_article$colour_group_name)
```
```{r}
unique(customer_1_article$index_name)

```

```{r}
unique(customer_1_article$product_group_name)

```
```{r}
```


```{r}
unique(customer_1_article$colour_group_name)
```



```{r}
freq_color_1 <- customer_1_article %>% group_by(color = colour_group_name) %>% summarise(Count = n())
```
```{r}
freq_color_1
```
```{r}
ggplot(aes(x= color, y= Count), data =freq_color_1) +geom_bar(stat = "identity", fill= "orange")
```
#### most color that customer A bought is Black, following white, lightpink

```{r}
freq_item_1 <- customer_1_article %>% group_by(group = product_group_name) %>% summarise(Count = n()) 
```

```{r}
freq_item_1
```
```{r}
ggplot(aes(x= group, y= Count), data =freq_item_1) +geom_bar(stat = "identity", fill = "orange")

```
```{r}
freq_producttype_1 <- customer_1_article %>% group_by(type = product_type_name) %>% summarise(Count = n())%>% arrange(desc(Count))

```
```{r}
freq_producttype_1
```
```{r}
ggplot(data = freq_producttype_1, aes(x=type, y= Count)) +geom_bar(stat ="identity", fill= "orange")
```
#### top items that customer 1 bought is underwear bottom and bra, following blouse and skirt. 

#### Buying pattern 

```{r}
customer_1_article
```

```{r}
freq_date_1 <- customer_1_article %>% group_by(Date) %>% summarise(Count =sum(Count))
```
```{r}
freq_date_1
```

```{r}
ggplot(aes(x= Date, y= Count), data = freq_date_1) +geom_point()+geom_line()
```


